Paper Replications

### 2025-10-23 inst/doc/Paper-Replications.Rmd
version 1.5.0

A thorough explanation on the usage of the additional functionalities of the *MultiATSM* package is available at the [package vignette](Guidelines.html).

@@

```{r, eval=FALSE}
# A) Load database data
LoadData("BR_2017")

@@

Economies <- c("U.S.") # Names of the economies from the economic system
GlobalVar <- c() # Global Variables
DomVar <- c("GRO", "INF") # Country-specific variables
N <- 3 # Number of spanned factors per country

@@

StatQ <- 0 # Stationary condition

@@

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(t0_sample, tF_sample, ModelType, Yields, GlobalMacroVar, DomesticMacroVar,
                           FactorLabels, Economies, DataFreq)

# 4) Optimization of the model
ModelPara <- Optimization(ATSMInputs, StatQ, DataFreq, FactorLabels, Economies, ModelType)
```

@@

```{r, echo= FALSE}
options(scipen = 100) # eliminate the scientific notation
data("BR_jps_gro_R3")
data("JPSrep")

RowsQ <- c("$r0$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$" )
TableQ <- data.frame(matrix(NA, ncol = 0, nrow =length(RowsQ)))
row.names(TableQ) <- RowsQ

PackageQ<- c(ModelPara$ests$r0, diag(ModelPara$ests$K1XQ))
BRq <- c(BR_jps_out$est.llk$rho0.cP, diag(BR_jps_out$est.llk$KQ.XX))
TableQ$MultiATSM <- PackageQ
TableQ$'BR (2017)' <- BRq

@@

```{r PdynTab, echo= FALSE}
data("BR_jps_gro_R3")
data("JPSrep")

RowsP <- c("PC1", "PC2", "PC3", "GRO", "INF")
ColP <- c(" ", RowsP)

# 1) K0Z and K1Z
# Bauer and Rudebusch coefficients
TablePbr <- data.frame(matrix(NA, ncol = length(ColP), nrow =length(RowsP)))
row.names(TablePbr) <- RowsP
colnames(TablePbr) <- ColP

TablePbr[[ColP[1]]] <- BR_jps_out$est.llk$KP.0Z
for(j in 1:length(RowsP) ){TablePbr[[RowsP[j]]] <- BR_jps_out$est.llk$KP.ZZ[,j]}

@@

# MultiATSM coefficients
TablePMultiATSM <- data.frame(matrix(NA, ncol = length(ColP), nrow =length(RowsP)))
row.names(TablePMultiATSM) <- RowsP
colnames(TablePMultiATSM) <- ColP

IdxVar <- c(3:5, 1:2) # indexes to flip the order of the spanned and unspanned factors
TablePMultiATSM[[ColP[1]]] <- ModelPara$ests$K0Z[IdxVar]
ModelPara$ests$K1Z <- ModelPara$ests$K1Z[IdxVar,IdxVar]
for(j in 1:length(RowsP) ){ TablePMultiATSM[[RowsP[j]]] <- ModelPara$ests$K1Z[,j]}

TablePMultiATSM <- round(TablePMultiATSM, digits = 5)
TableP <- rbind(TablePbr,TablePMultiATSM)
row.names(TableP) <- c(RowsP,paste(RowsP," ",sep="")) # trick to avoid rows to have the same name

kableExtra::kbl(TableP, align = "c", caption = "$P$-dynamics parameters") %>%
  kableExtra::kable_classic("striped", full_width = F)  %>%
  kableExtra::row_spec(0, font_size = 14) %>%
  kableExtra::add_header_above(c(" "= 1, "K0Z"=1, "K1Z" = 5), bold = T) %>%
  kableExtra::pack_rows("BR (2017)", 1, 5) %>%
  kableExtra::pack_rows("MultiATSM", 6, 10) %>%
  kableExtra::footnote(general = " $K0Z$ is the intercept and $K1Z$ is feedback matrix from the $P$-dynamics.")
```

```{r, echo= FALSE}
data("BR_jps_gro_R3")
data("JPSrep")

se <- data.frame(BR_jps_out$est.llk$sigma.e, ModelPara$ests$se )
rownames(se) <- "se"
colnames(se) <- c("MultiATSM","BR (2017)")
se <- round(se, digits = 7)

kableExtra::kbl(se, align = "c", caption ="Portfolio of yields with errors") %>%
  kableExtra::kable_classic("striped", full_width = F)  %>%
  kableExtra::row_spec(0, font_size = 14) %>%
  kableExtra::footnote(general = " $se$ is the standard deviation of the portfolio of yields observed with errors.")
```

For replicability, it is important to note that the $P-$dynamics results reported in Table \@ref(tab:PdynTab) for the *MultiATSM* package make use of the principal component weights provided by BR (2017). Such a matrix is simply a scaled-up version of the one provided by the function `pca_weights_one_country()` of this package. Accordingly, despite the numerical differences on the weight matrices, both methods generate time series of spanned factors which are perfectly correlated. Another difference between the two approaches relates to the construction form of the log-likelihood function (llk): while in the BR (2017) code the llk is expressed in terms of a portfolio of yields, the *MultiATSM* package generates this same input directly as a function of observed yields (i.e. both procedures lead to equivalent llk up to the Jacobian term).

# Candelon and Moura (forthcoming)

@@

OutputLabel <- "CM_jfec"
DataFreq <-"Monthly"

StatQ <- 0

# B.1) SPECIFIC model inputs
#################################### GVAR-based models ##################################################
GVARlist <- list( VARXtype = "unconstrained", W_type = "Sample Mean", t_First_Wgvar = "2004",
                  t_Last_Wgvar = "2019")
#################################### JLL-based models ###################################################
JLLlist <- list(DomUnit =  "China")
###################################### BRW inputs  ######################################################
WishBC <- 1
BRWlist <- within(list(flag_mean = TRUE, gamma = 0.001, N_iter = 200, B = 50, checkBRW = TRUE,
                       B_check = 1000),  N_burn <- round(N_iter * 0.15))

# C) Decide on Settings for numerical outputs
WishFPremia <- 1
FPmatLim <- c(24,36)

Horiz <- 25
DesiredGraphs <- c("GIRF", "GFEVD", "TermPremia")
WishGraphRiskFac <- 0
WishGraphYields <- 1
WishOrthoJLLgraphs <- 1

# D) Bootstrap settings
WishBootstrap <- 0 #  Set it to 1, if bootstrap is desired
BootList <- list(methodBS = 'bs', BlockLength = 4, ndraws = 3, pctg =  95)

# E) Out-of-sample forecast
WishForecast <- 1
ForecastList <- list(ForHoriz = 12,  t0Sample = 1, t0Forecast = 100, ForType = "Rolling")

@@

# 2) Minor preliminary work: get the sets of factor labels and  a vector of common maturities
FactorLabels <- LabFac(N, DomVar, GlobalVar, Economies, ModelType)
if(any(ModelType == c("GVAR single", "GVAR multi"))){ GVARlist$DataConnectedness <- TradeFlows}

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(t0_sample, tF_sample, ModelType, Yields, GlobalMacroVar, DomesticMacroVar,
                           FactorLabels, Economies, DataFreq, GVARlist, JLLlist, WishBC, BRWlist)

@@

# 5) Numerical and graphical outputs
# a) Prepare list of inputs for graphs and numerical outputs
InputsForOutputs <- InputsForOutputs(ModelType, Horiz, DesiredGraphs, OutputLabel, StatQ, DataFreq,
                                    WishGraphYields, WishGraphRiskFac, WishOrthoJLLgraphs, WishFPremia,
                                    FPmatLim, WishBootstrap, BootList, WishForecast, ForecastList)

# b) Fit, IRF, FEVD, GIRF, GFEVD, and Term Premia
NumericalOutputs <- NumOutputs(ModelType, ModelParaList, InputsForOutputs, FactorLabels, Economies)

# c) Confidence intervals (bootstrap analysis)
BootstrapAnalysis <- Bootstrap(ModelType, ModelParaList, NumericalOutputs, Economies, InputsForOutputs,
                               FactorLabels, JLLlist, GVARlist, WishBC, BRWlist)

# 6) Out-of-sample forecasting
Forecasts <- ForecastYields(ModelType, ModelParaList, InputsForOutputs, FactorLabels, Economies,
                            JLLlist, GVARlist, WishBC, BRWlist)
```

@@

Economies <- c("Brazil", "India", "Russia", "Mexico")
GlobalVar <- c("US_Output_growth", "China_Output_growth", "SP500")
DomVar <- c("Inflation","Output_growth", "CDS", "COVID")
N <- 2

@@

OutputLabel <- "CM_EM"
DataFreq <-"Weekly"

StatQ <- 0

# B.1) SPECIFIC model inputs
#################################### GVAR-based models ##################################################
GVARlist <- list( VARXtype = "constrained: COVID", W_type = "Sample Mean", t_First_Wgvar = "2015",
                  t_Last_Wgvar = "2020")
###################################### BRW inputs  ######################################################
WishBC <- 0

# C) Decide on Settings for numerical outputs
WishFPremia <- 1
FPmatLim <- c(47,48)

Horiz <- 12
DesiredGraphs <- c("GIRF", "GFEVD", "TermPremia")
WishGraphRiskFac <- 0
WishGraphYields <- 1
WishOrthoJLLgraphs <- 0

# D) Bootstrap settings
WishBootstrap <- 1 #  YES: 1; No = 0.
BootList <- list(methodBS = 'bs', BlockLength = 4, ndraws = 100, pctg =  95)

@@

# 2) Minor preliminary work: get the sets of factor labels and  a vector of common maturities
FactorLabels <- LabFac(N, DomVar, GlobalVar, Economies, ModelType)
GVARlist$DataConnectedness <- Trade_Flows

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(t0_sample, tF_sample, ModelType, Yields, GlobalMacro, DomMacro, FactorLabels,
                           Economies, DataFreq, GVARlist)

@@

# 5) Numerical and graphical outputs
# a) Prepare list of inputs for graphs and numerical outputs
InputsForOutputs <- InputsForOutputs(ModelType, Horiz, DesiredGraphs, OutputLabel, StatQ, DataFreq,
                                    WishGraphYields, WishGraphRiskFac, WishOrthoJLLgraphs, WishFPremia,
                                    FPmatLim, WishBootstrap, BootList)

# b) Fit, IRF, FEVD, GIRF, GFEVD, and Term Premia
NumericalOutputs <- NumOutputs(ModelType, ModelParaList, InputsForOutputs, FactorLabels, Economies)

# c) Confidence intervals (bootstrap analysis)
BootstrapAnalysis <- Bootstrap(ModelType, ModelParaList, NumericalOutputs, Economies, InputsForOutputs,
                               FactorLabels, JLLlist = NULL, GVARlist)

```

>>>>

A thorough explanation on the usage of the additional functionalities of the *MultiATSM* package are documented in the vignette **General Guidelines**.

@@

```{r}
# A) Load database data
LoadData("BR_2017")

@@

Economies <- c("US") # Names of the economies from the economic system
GlobalVar <- c() # Global Variables
DomVar <- c("GRO", "INF") # Country-specific variables
N <- 3 # Number of spanned factors per country

@@

StatQ <- FALSE # Stationary condition

@@

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(t0_sample, tF_sample, ModelType, Yields, GlobalMacroVar, DomesticMacroVar,
  FactorLabels, Economies, DataFreq,
  verbose = FALSE
)

# 4) Optimization of the model
ModelPara <- Optimization(ATSMInputs, StatQ, DataFreq, FactorLabels, Economies, ModelType,
  verbose = FALSE
)
```

@@

```{r, echo= FALSE}
options(scipen = 100) # eliminate the scientific notation

RowsQ <- c("$r0$", "$\\lambda_1$", "$\\lambda_2$", "$\\lambda_3$")
TableQ <- data.frame(matrix(NA, ncol = 0, nrow = length(RowsQ)))
row.names(TableQ) <- RowsQ

PackageQ <- c(ModelPara$`JPS original`$US$ModEst$Q$r0, diag(ModelPara$`JPS original`$US$ModEst$Q$K1XQ))
BRq <- c(BR_jps_out$est.llk$rho0.cP, diag(BR_jps_out$est.llk$KQ.XX))
TableQ$MultiATSM <- PackageQ
TableQ$"BR (2017)" <- BRq

@@

<a id="tab-PdynTab"></a>

```{r PdynTab, echo= FALSE}
RowsP <- c("PC1", "PC2", "PC3", "GRO", "INF")
ColP <- c(" ", RowsP)

# 1) K0Z and K1Z
# a) Bauer and Rudebusch coefficients
TablePbr <- data.frame(matrix(NA, ncol = length(ColP), nrow = length(RowsP)))
row.names(TablePbr) <- RowsP
colnames(TablePbr) <- ColP

TablePbr[[ColP[1]]] <- BR_jps_out$est.llk$KP.0Z
for (j in 1:length(RowsP)) {
  TablePbr[[RowsP[j]]] <- BR_jps_out$est.llk$KP.ZZ[, j]
}

@@

# b) MultiATSM coefficients
TablePMultiATSM <- data.frame(matrix(NA, ncol = length(ColP), nrow = length(RowsP)))
row.names(TablePMultiATSM) <- RowsP
colnames(TablePMultiATSM) <- ColP

# Estimate the P-dynamics using the weights provided by BR necessary for replication)
PP <- BR_jps_out$W[1:N, ] %*% Yields
ZZ <- rbind(PP, DomesticMacroVar)
Pdyncoef <- VAR(ZZ, "unconstrained")

TablePMultiATSM[[ColP[1]]] <- Pdyncoef$K0Z
for (j in 1:length(RowsP)) {
  TablePMultiATSM[[RowsP[j]]] <- Pdyncoef$K1Z[, j]
}

TablePMultiATSM <- round(TablePMultiATSM, digits = 5)
TableP <- rbind(TablePbr, TablePMultiATSM)
row.names(TableP) <- c(RowsP, paste(RowsP, " ", sep = "")) # trick to avoid rows to have the same name

kableExtra::kbl(TableP, align = "c", caption = "$P$-dynamics parameters") %>%
  kableExtra::kable_classic("striped", full_width = F) %>%
  kableExtra::row_spec(0, font_size = 14) %>%
  kableExtra::add_header_above(c(" " = 1, "K0Z" = 1, "K1Z" = 5), bold = T) %>%
  kableExtra::pack_rows("BR (2017)", 1, 5) %>%
  kableExtra::pack_rows("MultiATSM", 6, 10) %>%
  kableExtra::footnote(general = " $K0Z$ is the intercept and $K1Z$ is feedback matrix from the $P$-dynamics.")
```

```{r, echo= FALSE}
se <- data.frame(BR_jps_out$est.llk$sigma.e, ModelPara$`JPS original`$US$ModEst$Q$se)
rownames(se) <- "se"
colnames(se) <- c("MultiATSM", "BR (2017)")
se <- round(se, digits = 7)

kableExtra::kbl(se, align = "c", caption = "Portfolio of yields with errors") %>%
  kableExtra::kable_classic("striped", full_width = F) %>%
  kableExtra::row_spec(0, font_size = 14) %>%
  kableExtra::footnote(general = " $se$ is the standard deviation of the portfolio of yields observed with errors.")
```

For replicability, it is important to note that the $P-$dynamics results reported in [Table&nbsp;1.2](#tab-PdynTab) for the *MultiATSM* package make use of the principal component weights provided by BR (2017). Such a matrix is simply a scaled-up version of the one provided by the function `pca_weights_one_country()` of this package. Accordingly, despite the numerical differences on the weight matrices, both methods generate time series of spanned factors which are perfectly correlated. Another difference between the two approaches relates to the construction form of the log-likelihood function (llk): while in the BR (2017) code the llk is expressed in terms of a portfolio of yields, the *MultiATSM* package generates this same input directly as a function of observed yields (i.e. both procedures lead to equivalent llk up to the Jacobian term).

# Candelon and Moura (2024)

@@

OutputLabel <- "CM_jfec"
DataFreq <- "Monthly"
Folder2Save <- NULL

StatQ <- FALSE

# B.1) SPECIFIC model inputs
#################################### GVAR-based models ##################################################
GVARlist <- list(
  VARXtype = "unconstrained", W_type = "Sample Mean", t_First_Wgvar = "2004",
  t_Last_Wgvar = "2019", DataConnectedness = TradeFlows
)
#################################### JLL-based models ###################################################
JLLlist <- list(DomUnit = "China")
###################################### BRW inputs  ######################################################
WishBC <- TRUE
BRWlist <- within(list(
  Cent_Measure = "Mean", gamma = 0.001, N_iter = 200, B = 50, checkBRW = TRUE,
  B_check = 1000, Eigen_rest = 1
), N_burn <- round(N_iter * 0.15))

# C) Decide on Settings for numerical outputs
WishFPremia <- TRUE
FPmatLim <- c(24, 36)

Horiz <- 25
DesiredGraphs <- c("GIRF", "GFEVD", "TermPremia")
WishGraphRiskFac <- FALSE
WishGraphYields <- TRUE
WishOrthoJLLgraphs <- TRUE

# D) Bootstrap settings
WishBootstrap <- FALSE #  Set it to TRUE, if bootstrap is desired
BootList <- list(methodBS = "bs", BlockLength = 4, ndraws = 1000, pctg = 95)

# E) Out-of-sample forecast
WishForecast <- TRUE
ForecastList <- list(ForHoriz = 12, t0Sample = 1, t0Forecast = 100, ForType = "Rolling")

@@

# 2) Minor preliminary work: get the sets of factor labels and  a vector of common maturities
FactorLabels <- LabFac(N, DomVar, GlobalVar, Economies, ModelType)

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(
  t0_sample, tF_sample, ModelType, Yields, GlobalMacro, DomMacro,
  FactorLabels, Economies, DataFreq, GVARlist, JLLlist, WishBC, BRWlist
)

@@

# 5) Numerical and graphical outputs
# a) Prepare list of inputs for graphs and numerical outputs
InputsForOutputs <- InputsForOutputs(
  ModelType, Horiz, DesiredGraphs, OutputLabel, StatQ, DataFreq,
  WishGraphYields, WishGraphRiskFac, WishOrthoJLLgraphs, WishFPremia,
  FPmatLim, WishBootstrap, BootList, WishForecast, ForecastList
)

# b) Fit, IRF, FEVD, GIRF, GFEVD, and Term Premia
NumericalOutputs <- NumOutputs(
  ModelType, ModelParaList, InputsForOutputs, FactorLabels,
  Economies, Folder2Save
)

# c) Confidence intervals (bootstrap analysis)
BootstrapAnalysis <- Bootstrap(
  ModelType, ModelParaList, NumericalOutputs, Economies, InputsForOutputs,
  FactorLabels, JLLlist, GVARlist, WishBC, BRWlist, Folder2Save
)

# 6) Out-of-sample forecasting
Forecasts <- ForecastYields(
  ModelType, ModelParaList, InputsForOutputs, FactorLabels, Economies,
  JLLlist, GVARlist, WishBC, BRWlist, Folder2Save
)
```

@@

Economies <- c("Brazil", "India", "Russia", "Mexico")
GlobalVar <- c("US_Output_growth", "China_Output_growth", "SP500")
DomVar <- c("Inflation", "Output_growth", "CDS", "COVID")
N <- 2

@@

OutputLabel <- "CM_EM"
DataFreq <- "Weekly"
F2S <- NULL

StatQ <- FALSE

# B.1) SPECIFIC model inputs
#################################### GVAR-based models ##################################################
GVARlist <- list(
  VARXtype = "constrained: COVID", W_type = "Sample Mean", t_First_Wgvar = "2015",
  t_Last_Wgvar = "2020", DataConnectedness = TradeFlows_covid
)
###################################### BRW inputs  ######################################################
WishBC <- FALSE

# C) Decide on Settings for numerical outputs
WishFPremia <- TRUE
FPmatLim <- c(47, 48)

Horiz <- 12
DesiredGraphs <- c("GIRF", "GFEVD", "TermPremia")
WishGraphRiskFac <- FALSE
WishGraphYields <- TRUE
WishOrthoJLLgraphs <- FALSE

# D) Bootstrap settings
WishBootstrap <- TRUE #  YES: 1; No = 0.
BootList <- list(methodBS = "bs", BlockLength = 4, ndraws = 100, pctg = 95)

@@

# 2) Minor preliminary work: get the sets of factor labels and  a vector of common maturities
FactorLabels <- LabFac(N, DomVar, GlobalVar, Economies, ModelType)

# 3) Prepare the inputs of the likelihood function
ATSMInputs <- InputsForOpt(
  t0_sample, tF_sample, ModelType, Yields_covid, GlobalMacro_covid, DomMacro_covid, FactorLabels,
  Economies, DataFreq, GVARlist
)

@@

# 5) Numerical and graphical outputs
# a) Prepare list of inputs for graphs and numerical outputs
InputsForOutputs <- InputsForOutputs(
  ModelType, Horiz, DesiredGraphs, OutputLabel, StatQ, DataFreq,
  WishGraphYields, WishGraphRiskFac, WishOrthoJLLgraphs, WishFPremia,
  FPmatLim, WishBootstrap, BootList
)

# b) Fit, IRF, FEVD, GIRF, GFEVD, and Term Premia
NumericalOutputs <- NumOutputs(
  ModelType, ModelParaList, InputsForOutputs, FactorLabels,
  Economies, F2S
)

# c) Confidence intervals (bootstrap analysis)
BootstrapAnalysis <- Bootstrap(ModelType, ModelParaList, NumericalOutputs, Economies, InputsForOutputs,
  FactorLabels,
  JLLlist = NULL, GVARlist, WishBC, BRWlist, F2S
)
```
